### 2023-12-22 docs/projects/london-clojurians-dec-2023-talk/notebooks.combining_tools.qmd
moved docs for github pages

---
format:
  revealjs:
    theme: [default, src/notebooks/custom.scss]
    include-in-header: [text, <link rel="shortcut icon" href="Cookbook.svg" />]
    navigation-mode: vertical
    transition: slide
    background-transition: fade
    incremental: true
    output-file: notebooks.combining_tools-revealjs.html
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.combining_tools-revealjs_files/md-default0.js" type="text/javascript"></script><script src="notebooks.combining_tools-revealjs_files/md-default1.js" type="text/javascript"></script>
# Combining tools for data exploration

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: notebooks.combining_tools.html}
highlight-style: solarized

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="notebooks.combining_tools_files/md-default0.js" type="text/javascript"></script><script src="notebooks.combining_tools_files/md-default1.js" type="text/javascript"></script>
# Combining tools for data exploration

### 2023-12-22 docs/projects/visual-tools/clay-calva-demo-20231216/scratch.qmd
moved docs for github pages

---
format:
  revealjs: {theme: solarized, navigation-mode: vertical, transition: slide, background-transition: fade, incremental: true, output-file: scratch-revealjs.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scratch-revealjs_files/md-default1.js" type="text/javascript"></script><script src="scratch-revealjs_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="scratch-revealjs_files/vega3.js" type="text/javascript"></script><script src="scratch-revealjs_files/vega4.js" type="text/javascript"></script><script src="scratch-revealjs_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />

@@

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"scratch-revealjs_files\/0.csv","format":{"type":"csv"}}});</script></div>

>>>>

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scratch.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scratch_files/md-default1.js" type="text/javascript"></script><script src="scratch_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="scratch_files/vega3.js" type="text/javascript"></script><script src="scratch_files/vega4.js" type="text/javascript"></script><script src="scratch_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />

@@

<div><script>vegaEmbed(document.currentScript.parentElement, {"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"layer":[{"encoding":{"y":{"field":"petal-length","type":"quantitative"},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"circle","size":100,"tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300},{"encoding":{"y":{"field":"petal-length-prediction","type":"quantitative","axis":{"title":"petal-length"}},"opacity":{"value":0.5},"x":{"field":"petal-width","type":"quantitative"}},"mark":{"type":"line","size":10,"color":"brown","tooltip":true},"width":400,"background":"floralwhite","title":{"text":"R^2 = 0.927"},"height":300}],"height":300,"data":{"url":"scratch_files\/0.csv","format":{"type":"csv"}}});</script></div>

### 2023-12-22 docs/projects/visual-tools/clay-cider-demo-20231217/scratch-revealjs.qmd
moved docs for github pages

---
format:
  html: {toc: true, toc-depth: 4, theme: spacelab, output-file: scratch.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scratch_files/md-default13.js" type="text/javascript"></script><script src="scratch_files/md-default14.js" type="text/javascript"></script>

@@

<img src="scratch_files/0.png" style="width:100%;" />

@@

<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="scratch_files/0.png" style="width:100%;" /><img src="scratch_files/1.png" style="width:100%;" /></div><p>\]</p></div>

@@

<div><h3>raw image</h3><img src="scratch_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="scratch_files/2.png" style="width:100%;" /></div>

@@

<img src="scratch_files/3.png" style="width:100%;" />

@@

<img src="scratch_files/4.png" style="width:100%;" />

@@

<img src="scratch_files/5.png" style="width:100%;" />

@@

<div><p>(</p><div style="margin-left:10%;width:110%;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.7
</code></pre></div><img src="scratch_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
</code></pre></div><img src="scratch_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
</code></pre></div><img src="scratch_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
</code></pre></div><img src="scratch_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
</code></pre></div><img src="scratch_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
</code></pre></div><img src="scratch_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
</code></pre></div><img src="scratch_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>

>>>>

---
format:
  revealjs: {theme: solarized, navigation-mode: vertical, transition: slide, background-transition: fade, incremental: true, output-file: scratch-revealjs.html}
highlight-style: solarized
code-block-background: true
include-in-header: {text: '<link rel = "icon" href = "data:," />'}

---
<style>table {
  border-style: thin;
}
th, td {
  padding: 6px;
}
td {
  text-align: left;
}
th {
  text-align: center;
  background-color: #ddd;
}
tr:nth-child(even) {
  background-color: #f6f6f6;
}
</style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="scratch-revealjs_files/md-default13.js" type="text/javascript"></script><script src="scratch-revealjs_files/md-default14.js" type="text/javascript"></script>

@@

<img src="scratch-revealjs_files/0.png" style="width:100%;" />

@@

<div><p>\[</p><div style="margin-left:10%;width:110%;"><img src="scratch-revealjs_files/0.png" style="width:100%;" /><img src="scratch-revealjs_files/1.png" style="width:100%;" /></div><p>\]</p></div>

@@

<div><h3>raw image</h3><img src="scratch-revealjs_files/0.png" style="width:100%;" /><h3>darkened image</h3><img src="scratch-revealjs_files/2.png" style="width:100%;" /></div>

@@

<img src="scratch-revealjs_files/3.png" style="width:100%;" />

@@

<img src="scratch-revealjs_files/4.png" style="width:100%;" />

@@

<img src="scratch-revealjs_files/5.png" style="width:100%;" />

@@

<div><p>(</p><div style="margin-left:10%;width:110%;"><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.7
</code></pre></div><img src="scratch-revealjs_files/6.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.8
</code></pre></div><img src="scratch-revealjs_files/7.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">0.9
</code></pre></div><img src="scratch-revealjs_files/8.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1
</code></pre></div><img src="scratch-revealjs_files/9.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.1
</code></pre></div><img src="scratch-revealjs_files/10.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.2
</code></pre></div><img src="scratch-revealjs_files/11.png" style="width:100%;" /></div><p>\]</p></div><div><p>\[</p><div style="margin-left:10%;width:110%;"><div><pre><code class="language-clojure">1.3
</code></pre></div><img src="scratch-revealjs_files/12.png" style="width:100%;" /></div><p>\]</p></div></div><p>)</p></div>
